Experiment

### 2017-05-29 experiment.Rmd
New political knowledge question

*Q4.4*: How closely do you follow politics in the news?

@@

    - Extremely closely
    - Very closely
    - Closely
    - Barely
    - Not at all

>>>>

*Q4.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not. Others aren't that interested. Would you say that you follow what's going on in government and public affairs…

@@

    - Most of the time
    - Some of the time
    - Only now and then
    - Hardly at all
